---
title: Inshore Scallop Assessment Order of Operations
author: Brittany Wilson
date: 2021-05-18
output:
  word_document:
    toc: true
  html_document:
    toc: true
    theme: lumen
  pdf_document:
    toc: true
always_allow_html: true
---

```{r, include = FALSE}
require(usethis)
require(lubridate)
require(fs)
require(tidyverse)
require(flextable)
```


# Overview

This document is intended as a guide to the inshore scallop assessment workflow and to highlight the R-scripts that are used to facilitate the assessment process. This document can be used as a Rmarkdown allowing the user to open the required scripts within Rstudio, or be read as a word/PDF document where the user can review the workflow and manually locate the scripts witin the specified directory.

The inshore assessment is broken down by area:

**Bay of Fundy**: SPA1A, SPA1B, SPA3, SPA4 and SPA5, and SPA6

**SFA29W**: A, B, C, D, E


## Bay of Fundy


### 1. Standard Depth

  * Purpose: This script is used to pull bathymetry values from survey point locations and appends it to survey data. 
    
  * Path: Github ("https://github.com/Mar-scal/Inshore/blob/main/StandardDepth/Standardize_depth.R")
    
  * Output(s): Resulting file is called "towsdd_StdDepth_YYYY.csv
    
  * Saves to Directory: "ESS:/INSHORE SCALLOP/StandardDepth"
    

```{r, include = FALSE}
usethis::edit_file("C:/Users/WILSONB/Documents/GitHub/Inshore/StandardDepth/Standardize_depth.R")
```

### 2. Growth - Meat Weight Shell Height and Condition

  * Purpose:
    
  * Path: 
  
  * Output(s):
    
  * Saves to Directory: 

```{r, include = FALSE}
#year <- year(Sys.Date())-1 #Extract previous years folder structure for example
#dir_tree(path = paste0("Y:/INSHORE SCALLOP/BoF/", year, "/Assessment/Scripts/Growth")) #Prints out directory structure
usethis::edit_file("Y:/INSHORE SCALLOP/BoF/2020/Assessment/Scripts/Growth/BoF_MeatWeightShellHeight_2020.R")
usethis::edit_file("Y:/INSHORE SCALLOP/BoF/2020/Assessment/Scripts/Growth/SPA3_MeatWeightShellHeight_2020.R")
usethis::edit_file("Y:/INSHORE SCALLOP/BoF/2020/Assessment/Scripts/Growth/SPA6_MeatWeightShellHeight_2020.r")
```

### 3. Survey Indicies - Spatial plots

  * Purpose:
    
  * Path: 
  
  * Output(s):
    
  * Saves to Directory: 
  
  
  
### 4. Growth - Shell Height Frequencies, Biomass

  * Purpose:
    
  * Path: 
  
  * Output(s):
    
  * Saves to Directory: 