---
title: SFA29 West Scallop Assessment Script Workflow
author: Brittany Wilson
date: 2021-05-18
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    toc_collapsed: true
    number_sections: false
    theme: lumen
  pdf_document:
    toc: true
    includes:
      in_header: style.tex
always_allow_html: true
css: style.css
editor_options: 
  markdown: 
    wrap: 72
---

```{r Setup, include = FALSE}

require(usethis)
require(lubridate)
require(fs)
require(tidyverse)
require(flextable)
require(shinyWidgets)
#devtools::install_github("timelyportfolio/sweetalertR") #required for pop up reminders to save changes to github.
#require(sweetalertR)


#To use this Rmarkdown as a guide to run scripts, it requires you to have forked the Marscal Inshore repository (https://github.com/Mar-scal)

#Set working directory to *YOUR FORKED INSHORE REPOSITORY* (Not the Marscal master versions on ESS).
#dir <- ("https://github.com/Mar-scal/Inshore/tree/main/") #Github
dir <- "C:/Users/WILSONB/Documents/GitHub/Inshore" #Brittany
#dir <- () #Jamie
#dir <- () #Jessica

year <- 2022

#Remember to follow github workflow (i.e. commiting all changes with details (see commit protocol document (*To be made*)), pushing those changes up to your github forked repository and merging with the master Inshore repo on Marscal.
```

# Overview

This document is intended as a guide to the inshore scallop assessment
workflow and the R-scripts that are used in the assessment process. This
document can be used as a Rmarkdown allowing the user to open the
required scripts within Rstudio, or be read as a html or PDF document
where the user can review the workflow and manually locate the scripts
within the specified directory.

The SFA29 West assessment is separated by subareas:

A, B, C, D and E

# SFA29 West

## 1. Standard Depth

```{r Open Standardize_depth.R, eval =  FALSE, include = FALSE}
file.show(paste0(dir, "/Standardize_depth.R")) #Opens Standardize_depth.R
```

-   **Script Directory:**

    To be your forked Marscal Inshore repository path (e.g. `r dir`)

-   **Purpose:**

    This script is used to pull bathymetry values from survey point
    locations and appends it to survey data (i.e. standardize depth
    values).

-   **Output(s):**

    towsdd_StdDepth.csv

-   **Output Directory(s):**

    ESS:/Inshore/StandardDepth

------------------------------------------------------------------------

::: {.infobox .caution data-latex="{caution}"}
**COMMIT CHANGES**

Ensure that all changes made to the script Standardize_depth.R have been
saved and pushed to Marscal Inshore repository before continuing!
:::

------------------------------------------------------------------------

## 2. Intersecting data with scallop SDM layer

```{r Open Standardize_depth.R, eval =  FALSE, include = FALSE}
file.show(paste0(dir, "/SFA29W/SFA29_SDM_LWM.R")) #Opens SFA29_SDM_LWM.R
```

-   **Script Directory:**

    To be your forked Marscal Inshore repository path (e.g. `r dir`)

-   **Purpose:**

    This script is used for intersecting survey data with scallop species distribution model (SDM) layer (ESRI grid - sdm_utm_50)

-   **Output(s):**

    SFA29Tows_SDM.csv

-   **Output Directory(s):**

    ESS:/Inshore/SFA29/ScalSurv_SDM

------------------------------------------------------------------------

::: {.infobox .caution data-latex="{caution}"}
**COMMIT CHANGES**

Ensure that all changes made to the script SFA29_SDM_LWM.R have been
saved and pushed to Marscal Inshore repository before continuing!
:::

------------------------------------------------------------------------


## 2. Meat Weight - Shell Height and Condition modeling (Growth) {#meat-weight---shell-height-and-condition-modeling-growth}

```{r open MeatweightShellHeight.R files, eval =  FALSE, include = FALSE}

file.show(paste0("Y:/Inshore/SFA29/",year,"/Assessment/Scripts/Growth/SFA29_MeatWeightShellHeight_",year,".R")) 

#Eventually will be housed on github repo
file.show(paste0(dir, "/SFA29/Growth/SFA29_MeatWeightShellHeight.R"))

#$\bar{M}_{t+1} = \bar{\lambda}_{t+1}/ \bar{H}_{t+1}$
```

-   **Script Directory:**

    Y:/Inshore/SFA29/`r year`/Assessment/Scripts/Growth (eventually to be
    our forked Marscal/inshore repository, e.g.
    `r paste0(dir, "/SFA29/Growth")`)

-   **Purpose:**

    The SFA29_MeatWeightShellHeight.R scripts models meat weight with shell
    height, depth and tow.

-   **Overview:** 

<mark>Need to move files from previous year over:

Y:/Inshore/SFA29/YYYY/Assessment/Data/SurveyIndices/SFA29liveweight2014toYYYY.csv
Y:/Inshore/SFA29/YYYY/Assessment/Data/SurveyIndices/SFA29ConditionTimeseries2001toYYYY.csv

</mark>

1.  Set up data

2.  Run the Meat Weight Shell Height Model

4.  Condition data for Spatial plots

   
-   **Output(s):**

    -   **SFA29W**

        -   SFA29liveweight2014toYYYY.csv (MWTSH)
        
        -   SFA29liveweightYYYY.csv (MWTSH)

        -   SFA29W_ConditionTimeSeries2001toYYYY.csv (Condition)
        
        -   SFA29ConditionforMapYYYY.csv (Condition)

        -   SFA29growthYYYY.RData

        -   Figures: SFA29towdepthYYYY.png, MWTSH.29.YYYY.png,
            MWTSH.29.YYYY_towresid.png, and MWTSH.29.YYYY_towfit.png

        -   Model summary - MWTSHSFA29YYYY_ModelSummary.txt

   
\

-   **Output Directory(s):**

    -   **SFA29W**

        -   Y:/Inshore/SFA29/YYYY/Assessment/Data/SurveyIndices/
            (.csv)

    -   **Figures**

        -   Y:/Inshore/SFA29/YYYY/Assessment/Figures/Growth (.png)

        -   Y:/Inshore/SFA29/YYYY/Assessment/Figures (Condition time
            series .png)

------------------------------------------------------------------------

::: {.infobox .caution data-latex="{caution}"}
**COMMIT CHANGES**

Ensure that all changes made to scripts MeatWeightShellHeight.R for
SFA29 have been saved and pushed to Marscal Inshore repository before
continuing!
:::

------------------------------------------------------------------------

## 3. Spatial plots (Survey Indices)

```{r open Spatial plot scripts, eval =  FALSE, include = FALSE}
#year <- year(Sys.Date())-1 #Extract previous years folder structure for example
file.show(paste0(dir, "/SFA29/SurveyIndices/SFA29SpatialPlotsofSurveyData_pecjector.r"))

```

-   **Purpose:** Plot spatial patterns for Density, Biomass, Condition,
    Meat Count and Clapper data for SFA29W.

-   **Script Directory:** To be your forked Marscal Inshore repository
    path (e.g. `r paste0(dir, "/SFA29/SurveyIndicies")`)

-   **Output(s):**

    -   Spatial plots for each area and commercial, recruit and
        pre-recruit size ranges

        -   Density - ContPlot_SFA29_ComDensityYYYY.png,
            ContPlot_SFA29_RecDensityYYYY.png,
            ContPlot_SFA29_PreDensityYYYY.png

        -   Biomass - ContPlot_SFA29_ComBiomassYYYY.png,
            ContPlot_SFA29_RecBiomassYYYY.png,
            ContPlot_SFA29_PreBiomassYYYY.png

        -   Condition - ContPlot_SFA29_ConditionYYYY.png (using only
            commercial sizes)

        -   Meat Count - ContPlot_SFA29_MeatcountYYYY.png (using only
            commercial sizes)

        -   Clappers and Clapper proportion -
            ContPlot_SFA29_ComClappersYYYY.png,
            ContPlot_SFA29_RecClappersYYYY.png,
            ContPlot_SFA29_PropComClappersYYYY.png,
            ContPlot_SFA29_PropRecClappersYYYY.png

-   **Output Directory(s):** Y:/Inshore/SFA29/YYYY/Assessment/Figures

------------------------------------------------------------------------

::: {.infobox .caution data-latex="{caution}"}
**COMMIT CHANGES**

Ensure that all changes made to SFA29SpatialPlotsofSurveyData_pecjector.r
have been saved and pushed to Marscal Inshore repository before
continuing!
:::

------------------------------------------------------------------------

## 4. VonB (Growth)

```{r Open SFA28W_VonB_YYYY.R, eval =  FALSE, include = FALSE}

file.show(paste0("Y:/Inshore/SFA29/",year,"/Assessment/Scripts/Growth/SFA29W_VonB_",year,".R")) #Script for SPA 1A, 1B, 4 and 5 (last updated 2016).

#file.show(paste0(dir, "/SFA29/Growth/SFA29W_VonB_YYYY.R"))

```

-   **Purpose:** These scripts model growth using the von-Bertalanffy
    growth equation for specified cruise.

    **NOTE:** This script does not need to be run every year. New aging
    data is required for updated outputs.

-   **Overview:**

Set up data for modelling: - Query detailed meat weight/shell height
sampling data from database (scallsur.scwgthgt) for specified cruise. - Format data for the model - Run the VonB

<center>

$L_t = L_\infty(1-e^{-K(t)})$

</center>

Where:

$L_t$ = Length at age $t$

$L_\infty$ = asymptotic length (length at which growth rate is zero) -
estimated from the data

$K$ = Brody growth coeff (rate of growth towards asymptote) - estimated
from the data

$t$ = scallop age (years)

-   **Script Directory:** To be your forked Marscal Inshore repository
    path (e.g. `r paste0(dir, "/SFA29/Growth")`)

-   **Output(s):**

-   **Output Directory(s):**

------------------------------------------------------------------------

::: {.infobox .caution data-latex="{caution}"}
**COMMIT CHANGES**

Ensure that all changes made to VonB.R script has been saved and
pushed to Marscal Inshore repository before continuing!
:::

------------------------------------------------------------------------

## 5. Shell Height Frequencies (Growth) {#shell-height-frequencies-growth}

```{r Open SFA29_SHF_YYYY.R, eval = FALSE, include = FALSE}

file.show(paste0("Y:/Inshore/SFA29/",year,"/Assessment/Scripts/Growth/SFA29_SHF_",year,".R"))

#file.show(paste0(dir, "/SFA29/Growth/SFA29_SHF.R"))

```

-   **Purpose:** This script produces plots of shell height frequencies
    for SFA29W by subarea by year, and calculates commercial mean shell
    height in year t ($\bar{L}$) and uses parameters from the VonB
    growth model to predict how much a shell of height $L$ will grow in
    one year.

-   **Overview:**

    -   Query shell height bin data from database (scallsur.scliveres)
        for specified Subareas.

    -   Calculate stratified shell height frequency by year

    -   Plot shell height frequencies for each year (last 7 years)

    -   Calculate $\bar{L}$ for all of Subareas by year for commercial and recruit sizes

    -   Predict $\bar{L}$ in $t+1$:

    <center>

    $\bar{L}_{t+1} = L_\infty * (1-e^{-e^{logK}}) + (e^{-e^{logK}}) * (\bar{L})$

    </center>

    -   Calculate $\bar{L}$ for each subarea for plotting


-   **Script Directory:** To be your forked Marscal Inshore repository
    path (e.g. `r paste0(dir, "/SFA29/Growth")`)

-   **Output(s):** - Shell Height Frequency plots for each year by
    subarea

    -   SHF_SFA29SUBAREA.png

    -   Plot of Commercial mean SH by year ($\bar{L}$) -
            SFA29.lbar.comm.png
            
    -   Plot of Recruit mean SH by year ($\bar{L}$) -
            SFA29.lbar.rec.png


    -   Saved objects for predicting mean weight -
            SFA28.SHobj.YYYY.csv


-   **Output Directory(s):**

    -   Y:/Inshore/SFA29/YEAR/Assessment/Figures (.png)

    -   Y:/Inshore/SFA29/YEAR/Assessment/Data/Growth (.csv)

------------------------------------------------------------------------

::: {.infobox .caution data-latex="{caution}"}
**COMMIT CHANGES**

Ensure that all changes made to SHF.R scripts have been saved and pushed
to Marscal Inshore repository before continuing!
:::

------------------------------------------------------------------------


## 6. Growth Rates (Growth)

```{r Open GrowthRates_Actual.R, eval =  FALSE, include = FALSE}

file.show(paste0("Y:/Inshore/SFA29/",year,"/Assessment/Scripts/Growth/GrowthRate_Actual.R"))

```

-   **Purpose:** Saves Predicted and Actual growth rates for commercial
    ($g$) and recruit ($gR$) sized scallops.

**NOTE:** This script requires inputs from [2. Meat Weight - Shell
Height and Condition modeling
(Growth)](#meat-weight---shell-height-and-condition-modeling-growth) and
[5. Shell Height Frequencies (Growth)](#shell-height-frequencies-growth)

-   **Overview:**

    -   Import outputs from previous scripts e.g.SFA29.SHobj.YYYY.R, 
        SFA29growthYYYY.RData, growth.actual.2001toYYYY.csv
        

    -   Imports predicted and actual shell height, MWSH.YYYY model, and
        meat weight shell height data from samples.

        **Actual Growth Rates**

    -   commercial mean meat weight in year t-1 is predicted using
        predicted SH (SH predicted from year t-1 to year t) and actual
        mw/sh relationship in year t

    -   recruit mean meat weight in year t-1 is predicted using
        predicted SH (SH predicted from year t-1 to year t) and actual
        mw/sh relationship in year t

    -   actual commercial mean meat weight in year t is predicted and

    -   actual recruit mean meat weight in year t is predicted.

        **Predicted Growth Rates**

    -   Calculate mean weight of commercial and recruit animals:

        1\. In year t ("actual") using mean SH in year t and meat weight
        shell height relationship in year t

        2\. In year t+1 ("pred") using predicted mean SH in year t+1
        (predicted from year t) and meat weight shell height
        relationship in year t

    -   i.e. predicted g and gR were from year t to t+1, assuming it is
        unknown.

    <center>

    $g_{t-1} = \bar{w_t}/\bar{w}_{t-1}$

    </center>

-   **Script Directory:** To be your forked Marscal Inshore repository
    path (e.g. `r paste0(dir, "/SFA29/Growth")`)

-   **Output(s):**

        -   growth.actual.2001toYYYY.csv

        -   SFA29W.GrowthRate.Commercial.Actual.png

        -   SFA29W.GrowthRate.Recruit.Actual.png


-   **Output Directory(s):**

    -   Y:/Inshore/SFA29/Figures (.png)

    -   Y:/Inshore/SFA29/Assessment/Data/Growth (.csv)

------------------------------------------------------------------------

::: {.infobox .caution data-latex="{caution}"}
**COMMIT CHANGES**

Ensure that all changes made to GrowthRate_Actual.R scripts have been
saved and pushed to Marscal Inshore repository before continuing!
:::

------------------------------------------------------------------------

## 8. Numbers per tow - Survey Estimates - LIVE/DEAD (Survey Indices)

```{r Open scallopSurvEstimates_SDM_LIVEYYYY.R, eval =  FALSE, include = FALSE}

file.show(paste0("Y:/Inshore/SFA29/",year,"/Assessment/Scripts/SurveyIndices/scallopSurvEstimates_SDM_LIVE.R"))
file.show(paste0("Y:/Inshore/SFA29/",year,"/Assessment/Scripts/SurveyIndices/scallopSurvEstimates_SDM_DEAD.R"))

```

-   **Purpose:** Calculates population numbers (numbers scaled to total
    area) and biomass indices.

**NOTE:** This script requires inputs from SFA29Tows_SDM.csv, SFA29_SDM_LWM.R and SFA29W_model_areas_towable_units.csv 
(saved under Scripts/model directory). 

-   **Overview:**

    -   

        -   

    -   

        -   
        
        "rh" - recruit numbers scaled to respective SDM strata in millions 
        "obs.nu" recruit numbers per tow CV
        "L" commercial number scaled to respective SDM strata in millions

-   **Script Directory:** To be your forked Marscal Inshore repository
    path (e.g. `r paste0(dir, "/SFA29/SurveyIndices")`)

-   **Output(s):**

    -   SDM.HighMedLow.2001toYYYY.Numbers.csv/ SDM.HighMedLow.2001toYYYY.Clappers.csv / SDM.HighMedLow.2001toYYYY.Clapper.Proportion.csv

    -   SDM.StratifiedEstimates.2001toYYYY.Numbers.csv/ SDM.StratifiedEstimates.2001toYYYY.Clappers.csv

    -   rh.obs.nu.2001toYYYY.csv 

    -   L.2001toYYYY.csv
    
    -   SFA29SUBAREA.Numberspertow.YYYY.png
    
    -   SFA29AtoD.Numberspertow.Prerecruit.YYYY.png
    
     -   SFA29AtoD.Numberspertow.Recruit.YYYY.png
     
    -   SFA29AtoD.Numberspertow.Commercial.YYYY.png
    
    -   SubareaE.ExploratoryMeanbyTow.Numbers.YYYY.csv
    
    -   SFA29E.Numberspertow.YYYY.png
    
    -   SDM_SampleSize.YYYY.csv
    
    -   SFA29.SDM.SampleSize.YYYY.png
    
    -   SFA29.AtoD.stratified.YYYY.png
    
    -   SFA29AtoD.Clappers.Prop.Commercial.YYYY.png
    
    -   SFA29AtoD.Clappers.Prop.Recruit.YYYY.png
    
    -   SFA29AtoD.Clappers.Prop.Prerecruit.YYYY.png
    
    -   SFA29.all.tows.2001toYYYY.Proportion.Dead.csv

-   **Output Directory(s):**

    -   Y:/Inshore/SFA29/Figures (.png)

    -   Y:/Inshore/SFA29/Assessment/Data/SurveyIndices (.csv)

------------------------------------------------------------------------

::: {.infobox .caution data-latex="{caution}"}
**COMMIT CHANGES**

Ensure that all changes made to AREA_NumbersWeightperTow_YYYY.r scripts
have been saved and pushed to Marscal Inshore repository before
continuing!
:::

------------------------------------------------------------------------

## 8. Weight per tow - Survey Estimates (Survey Indices)

```{r Open scallopSurvEstimates_WeightPerTow.R,  eval =  FALSE, include = FALSE}

file.show(paste0("Y:/Inshore/SFA29/",year,"/Assessment/Scripts/SurveyIndices/scallopSurvEstimates_WeightPerTow.R"))

```

-   **Purpose:**

    -   
        
  **NOTE:** This script requires inputs from SFA29W_model_areas_towable_units.csv 
        (saved under Scripts/model directory).
        
        <mark>Need to move files from previous year over:

Y:/Inshore/SFA29/YYYY/Assessment/Data/SurveyIndices/SurveymeanwgttowSFA29_2001toYYYY.csv

-   **Overview:**

    -   

    -   

-   **Script Directory:** To be your forked Marscal Inshore repository
    path (e.g. `r paste0(dir, "/SFA29/SurveyIndices")`)

    

-   **Output(s):**

    -   

    -   

    -   

    -   

-   **Output Directory(s):**

    -   

    -   

------------------------------------------------------------------------

::: {.infobox .caution data-latex="{caution}"}
**COMMIT CHANGES**

Ensure that all changes made to scallopSurvEstimates_WeightPerTow.R scripts have been saved
and pushed to Marscal Inshore repository before continuing!
:::

------------------------------------------------------------------------

## 10. Lobster Survey Estimates (Survey Indices)

```{r Open SurveyEstimates_Lobster_SDM.r, eval =  FALSE, include = FALSE}

file.show(paste0("Y:/Inshore/SFA29/",year,"/Assessment/Scripts/SurveyIndices/SurveyEstimates_Lobster_SDM.r"))

```

-   **Purpose:** 


-   **Overview:**

    -   

    -  

        -   

    -   

        -  
        
    -   
        
    -   
    

-   **Script Directory:** To be your forked Marscal Inshore repository
    path (e.g. `r paste0(dir, "/SFA29/SurveyIndices")`)

-   **Output(s):**

    -   

    -   

    -   

-   **Output Directory(s):**

    -  

    -   

------------------------------------------------------------------------

::: {.infobox .caution data-latex="{caution}"}
**COMMIT CHANGES**

Ensure that all changes made to AREA_RatioLinedUnlined_YYYY.r scripts
have been saved and pushed to Marscal Inshore repository before
continuing!
:::

------------------------------------------------------------------------

## 11. Model (Model)

-   **Purpose:**

    -   Population model - Bayesian state space model

        <center>

        $B_{t+1} = (e^{-m_t}g_t(B_t-C_t)+e^{-m_t}g_{Rt}R_t)\tau_t$

        </center>

-   **Overview:**

    -   Model formulation for BoF: have biomass remove catch then grow
        up and kill off.

    -   Starts by creating comparison file (SPAx_ModelData_R.xlsx).
        Ensure previous years data has not changed. Investigate if
        differences are flagged.

    -   Import data from generated SPAx_ModelData_R\_YYYY-MM-DD.xlsx :

        -   C - Catch

        -   N - population numbers

        -   I - Biomass scaled to full area

        -   I.cv -

        -   IR - Recruit Biomass scaled to full area

        -   IR.cv -

        -   ratiolined - ratio of lined to unlined

        -   g - Commercial growth

        -   gR - recruit growth

        -   clappers - clapper numbers

    -   Set parameters to be returned from the winbugs model run:

        -   B - Commercial Biomass (in tonnes)

        -   R - Recruit Biomass (in tonnes)

        -   q - Catchability

        -   K - Scaling parameter

        -   P - Biomass scaled by K

        -   **sigma**

        -   S - dissolution factor (factors into the clapper model)

        -   m - mortality

        -   **kappa.tau - observation error for clappers?**

        -   r - recruit biomass scaled by K

        -   Fmort - instant mortality

        -   mu - exploitation rate

        -   Irep - Commercial Biomass not scaled by q

        -   IRrep - Recruit Biomass not scaled by q

        -   Presid, sPresid, Iresid, IRresid, sIresid, sIRresid -
            residuals

    -   Model is run in Winbugs and diagnostics are run (i.e. checks for
        model convergence)

    -   Plots of time series of survey biomass estimates are made

    -   Plots biomass time series (EN/FR), box plot contains 80% of the
        data when pred.lim = 0.2 (i.e. 80% of the data is located
        between the whiskers)

    -   Plot of the posteriors

    -   Plots of residuals

    -   Plot of the predicted prediction-evaluation

    -   Creates decision table and saves out model summary.

-   **Script Directory:** To be your forked Marscal Inshore repository
    path (e.g. `r paste0(dir, "/BoF/Model")`)

-   **Output(s):**

    -   SPAx_ModelData_R.xlsx

    -   SPAx_Model_YYYY.RData

    -   spaXModelOutput.csv

    -   Survey_est_figure_AREA.png

    -   Model_biomass_figure_AREA.png

    -   plot.Presids_AREA.png, plot.sPresid_AREA.png,
        plot.Iresid_AREA.png. plot.IRresid_Area.png

    -   Prediction_evaluation_figure_predicted_AREA.png

    -   Prediction_evaluation_figure_actual_AREA.png

    -   decisiontableYYYY_AREA.csv

    -   SPA6_Model_YYYY.RData

    -   Model_results_and_diagnostics_YYYY_AREA.RData

-   **Output Directory(s):**

    -   Y:/Inshore/BoF/Model/AREA

------------------------------------------------------------------------

::: {.infobox .caution data-latex="{caution}"}
**COMMIT CHANGES**

Ensure that all changes made to Model scripts have been saved and pushed
to Marscal Inshore repository before continuing!
:::

------------------------------------------------------------------------
