---
title: Inshore Scallop Assessment Order of Operations
author: Brittany Wilson
date: 2021-05-18
output:
  html_document:
    toc: true
    theme: lumen
  pdf_document:
    toc: true
    includes:
      in_header: style.tex
always_allow_html: true
css: style.css
---

```{r Setup, include = FALSE}

require(usethis)
require(lubridate)
require(fs)
require(tidyverse)
require(flextable)
require(shinyWidgets)
#devtools::install_github("timelyportfolio/sweetalertR") #required for pop up reminders to save changes to github.
require(sweetalertR)


#To use this Rmarkdown as a guide to run scripts, it requires you to have forked the Marscal Inshore repository (https://github.com/Mar-scal)

#Set working directory to *YOUR FORKED INSHORE REPOSITORY* (Not the Marscal master versions on ESS).
#dir <- ("https://github.com/Mar-scal/Inshore/tree/main/") #Github
dir <- ("C:/Users/WILSONB/Documents/GitHub/Inshore") #Brittany
#dir <- () #Jamie
#dir <- () #Jessica

#Remember to follow github workflow (i.e. commiting all changes with details (see commit protocol document (not yet made)), pushing those changes up to your github forked repository and merging with the master Inshore repo on Marscal.
```


# Overview

This document is intended as a guide to the inshore scallop assessment workflow and to highlight the R-scripts that are used to facilitate the assessment process. This document can be used as a Rmarkdown allowing the user to open the required scripts within Rstudio, or be read as a html or PDF document where the user can review the workflow and manually locate the scripts witin the specified directory.

The inshore assessment is separated by area:

**Bay of Fundy**: SPA1A, SPA1B, SPA3, SPA4 and SPA5, and SPA6

**SFA29W**: A, B, C, D, E


# Bay of Fundy


## 1. Standard Depth

```{r Open Standardize_depth.R, include = FALSE}
usethis::edit_file(paste0(dir, "/StandardDepth/Standardize_depth.R")) #Opens Standardize_depth.R
```

  * **Path:** 
  
      To be your forked Marscal Inshore repository path (e.g. `r paste0(dir, "/StandardDepth")` )

  * **Purpose:** 
  
      This script is used to pull bathymetry values from survey point locations and appends it to survey data (i.e. standardize depth values). 
    
  * **Output(s):** 
  
      towsdd_StdDepth.csv
    
  * **Output Directory(s):** 
  
      ESS:/INSHORE SCALLOP/StandardDepth
    
-------------------------------------------------------------------------

::: {.infobox .caution data-latex="{caution}"}
**COMMIT CHANGES**

Ensure that all changes made to the script Standardize_depth.R have been saved and pushed to Marscal Inshore repository before continuing!
:::

-------------------------------------------------------------------------


## 2. Growth - Meat Weight Shell Height and Condition

```{r open MeatweightShellHeight.R files, include = FALSE}
#year <- year(Sys.Date())-1 #Extract previous years folder structure for example
#dir_tree(path = paste0("Y:/INSHORE SCALLOP/BoF/", year, "/Assessment/Scripts/Growth")) #Prints out directory structure

usethis::edit_file("Y:/INSHORE SCALLOP/BoF/2020/Assessment/Scripts/Growth/BoF_MeatWeightShellHeight_2020.R") #Script for SPA 1A, 1B, 4 and 5.
usethis::edit_file("Y:/INSHORE SCALLOP/BoF/2020/Assessment/Scripts/Growth/SPA3_MeatWeightShellHeight_2020.R") #Script for SPA 3
usethis::edit_file("Y:/INSHORE SCALLOP/BoF/2020/Assessment/Scripts/Growth/SPA6_MeatWeightShellHeight_2020.r") #Script for SPA 6

#Eventually will be housed on github repo ???
#usethis::edit_file(paste0(dir, "/Growth/BoF_MeatWeightShellHeight.R"))
#usethis::edit_file(paste0(dir, "/Growth/SPA3_MeatWeightShellHeight.R"))
#usethis::edit_file(paste0(dir, "/Growth/SPA6_MeatWeightShellHeight.r"))
```


  * **Path:** 
  
      Y:/INSHORE SCALLOP/BoF/2020/Assessment/Scripts/Growth 
      (eventually to be our forked Marscal/inshore repository, e.g. `r paste0(dir, "/Growth")`)
    
  * **Purpose:** 
  
      The MeatWeightShellHeight.R scripts predicts meat weight with shell height and depth.
  
  * **Output(s):** 
  
    - **SPA 1A, 1B, 4 and 5**
      
      - BFliveweight.csv  (MWTSH)
    
      - BFConditionforMap.csv (Condition)
      
      - BFgrowthYYYY.RData
      
      - Figures: BFtowdepthYYYY.png, MWTSHBFYYYY.png, MWTSHBFYYYY_towresid.png, and MWTSHBFYYYY_towfit.png
      
    - **SPA 3**
    
      - BIliveweight.csv (MWTSH)
    
      - BIConditionforMap.csv (Condition)
      
      - BIgrowthYYYY.RData
      
      - Figures: BItowdepthYYYY.png, MWTSHBIYYYY.png, MWTSHBIYYYY_towresid.png, and MWTSHBIYYYY_towfit.png
    
    - **SPA 6**
    
      - GMliveweight.csv (MWTSH)
    
      - GMConditionforMap.csv (Condition)
      
      - GMgrowthYYYY.RData
      
      - Figures: GMtowdepthYYYY.png, MWTSHGMYYYY.png, MWTSHGMYYYY_towresid.png, and MWTSHGMYYYY_towfit.png
      
    - **Other**
    
      - AREA_ConditionTimeSeries.png (Condition Time series)


    
  * **Output Directory(s):** 
  
    - **SPA 1A, 1B, 4 and 5**
    
      - Y:/INSHORE SCALLOP/BoF/YYYY/Assessment/Data/SurveyIndices/SPA1A1B4and5 (.csv)
      
    - **SPA 3** 
    
      - Y:/INSHORE SCALLOP/BoF/YYYY/Assessment/Data/SurveyIndices/SPA3 (.csv)
      
    - **SPA 6** 
    
      - Y:/INSHORE SCALLOP/BoF/YYYY/Assessment/Data/SurveyIndices/SPA6 (.csv)
      
    - **Figures**
    
      - Y:/INSHORE SCALLOP/BoF/YYYY/Assessment/Figures/Growth (.png)
      
      - Y:/INSHORE SCALLOP/BoF/YYYY//Assessment/Figures (Condition time series .png)
      
     
-------------------------------------------------------------------------

::: {.infobox .caution data-latex="{caution}"}
**COMMIT CHANGES**

Ensure that all changes made to scripts MeatWeightShellHeight.R for each SPA have been saved and pushed to Marscal Inshore repository before continuing!
:::

-------------------------------------------------------------------------


## 3. Survey Indicies - Spatial plots

```{r open Spatial plot scripts, include = FALSE}
#year <- year(Sys.Date())-1 #Extract previous years folder structure for example
usethis::edit_file(paste0(dir, "/SurveyIndices/BoFSpatialPlotsofSurveyData_pecjector.r"))
usethis::edit_file(paste0(dir, "/SurveyIndices/SFA29_SpatialPlots_pecjector.r"))
```


  * **Purpose:** Plot spatial patterns for Density, Biomass, Condition, Meat Count and Clapper data for the Full Bay of Fundy extent, SPA1A, 1B, 3, 4 and 5, and 6.
    
  * **Path:** To be your forked Marscal Inshore repository path (e.g. C:/Users/WILSONB/Documents/GitHub/Inshore/SurveyIndicies)
  
  * **Output(s):**
  
    - **Spatial plots for each area and commercial, recruit and pre-recruit size ranges**
    
      - Density - ContPlot_SPA#_ComDensityYYYY.png, ContPlot_SPA#_RecDensityYYYY.png, ContPlot_SPA#_PreDensityYYYY.png
      
      - Biomass - ContPlot_SPA#_ComBiomassYYYY.png, ContPlot_SPA#_RecBiomassYYYY.png, ContPlot_SPA#_PreBiomassYYYY.png
      
      - Condition - ContPlot_SPA#_ConditionYYYY.png (using only commercial sizes)
      
      - Meat Count - ContPlot_SPA#_MeatcountYYYY.png (using only commercial sizes)
      
      - Clappers and Clapper proportion - ContPlot_SPA#_ComClappersYYYY.png, ContPlot_SPA#_RecClappersYYYY.png,
                                          ContPlot_SPA#_PropComClappersYYYY.png, ContPlot_SPA#_PropRecClappersYYYY.png
      
  
  * **Output Directory(s):** Y:/INSHORE SCALLOP/BoF/YYYY/Assessment/Figures

  
-------------------------------------------------------------------------

::: {.infobox .caution data-latex="{caution}"}
**COMMIT CHANGES**

Ensure that all changes made to BoFSpatialPlotsofSurveyData_pecjector.r have been saved and pushed to Marscal Inshore repository before continuing!
:::

-------------------------------------------------------------------------


## 4. Growth - Shell Height Frequencies, Biomass

  * **Purpose:**
    
  * **Path:** 
  
  * **Output(s):**
    
  * **Output Directory(s):** 